Identifying the L1 of non-native writers: the CMU-Haifa system\\[1em] {\large Chris Dyer$^\ast$ Manaal Faruqui$^\ast$ Noam Ordan$^\dagger$ Nathan Schneider$^\ast$\\ Yulia Tsvetkov$^\ast$ Naama Twitto$^\dagger$ Shuly Wintner$^\dagger$}\\[-3em]

### 2013-04-06 paper/paper.tex
updated Restored

\begin{compactdesc}
\item[POS $n$-grams] Part-of-speech $n$-grams were used in various
  text-classification tasks.
\item[Prompt] Since the prompt contributes information on the domain,
  it is likely that some words (and, hence, character sequences) will
  occur more frequently with some prompts than with others. We
  therefore use the prompt ID in conjunction with other features.
\item[Document length] The number of tokens in the text is highly
  correlated with the author's level of fluency, which in turn is
  correlated with the author's L1.
\item[Pronouns] The use of pronoun varies greatly among different
  authors. We use the same list of~25 English pronouns that
  \citet{vered:noam:shuly} use for identifying translationese.
\item[Punctuation] Similarly, different languages use punctuation
  differently, and we expect this to taint the use of punctuation in
  non-native texts.
\item[Passives] English uses passive voice more frequently than other
  languages. Again, the use of passives in L2 can be correlated with
  the author's L1.
\item[Positional token frequency] The choice of the first and last few
  words in a sentence is highly constrained, and may be significantly
  influenced by the author's L1.
\item[Cohesive markers] These are 40 function words (and short
  phrases) that have a strong discourse function in texts (`however',
  `because', `in fact', etc.) Translators tend to spell out implicit
  utterances and render them explicitly in the target text
  \citep{Blum-Kulka:1986}. We use the list
  of~\citet{vered:noam:shuly}.
\item[Cohesive verbs] This is a list of manually compiled verbs that
  are used, like cohesive markers, to spell out implicit utterances
  (`indicate', `imply', `contain', etc.)
\item[Function words] Frequent tokens, which are mostly function
  words, have been used successfully for various text classification
  tasks. \citet{koppel-ordan:2011:ACL-HLT2011} define a list of 400
  such words, of which we only use~100 (using the entire list was not
  significantly different).
\item[Contextual function words] To further capitalize on the ability
  of function words to discriminate, we define pairs consisting of a
  function word from the list mentioned above, along with the POS tag
  of its adjacent word. This feature captures patterns such as verbs
  and the preposition or particle immediately to their right, or nouns
  and the determiner that precedes them. We also define 3-grams
  consisting of one or two function words and the POS tag of the third
  word in the 3-gram.
\item[Lemmas] The content of the text is not considered a good
  indication of the author's L1, but many text categorization tasks
  use lemmas (more precisely, the stems produced by the tagger) as
  features approximating the content.
\item[Misspelling features] Clearly, the spelling errors that learners
  make in English depend on the phonological properties of their
  L1. \sw{???}
\item[Restored tags] We focus on three important token classes defined
  above: punctuation marks, function words and cohesive verbs. We
  first remove words in these classes from the texts, and then recover
  the most likely hidden POS tags in a sequence of words, according to
  an $n$-gram language model trained on all essays in the training
  corpus corrected with a spell checker and containing both words and
  hidden tags. This feature should capture specific words or
  punctuation marks that are consistently omitted (deletions), or
  misused (insertions, substitutions). To restore hidden tags we use
  the \texttt{hidden-ngram} utility provided in SRILM
  \citep{stolcke02srilm}.
\item[Brown clusters] \sw{???}
\end{compactdesc}

@@

\begin{compactdesc}
\item[\feat{DocLen}] Document length in tokens. 11.81\%.
\item[\feat{Punct}] Counts of each punctuation mark. 27.41\%.
\item[\feat{Pron}] Counts of each pronoun. 22.81\%.
\item[\feat{Position}] Positional token frequency. We use the counts
  for the first two and last three words before the period in each
  sentence as features. 53.03\%.
\item[\feat{PsvRatio}] The proportion of passive verbs out of all
  verbs. 12.26\%.
\item[\feat{CxtFxn}] Contextual function words. Bi-grams yield
  62.79\%, tri-gram 62.32\%.
\item[\feat{Misspell}] Spelling correction edits. \sw{???}. 37.29\%.
\item[\feat{Restore}] Counts of substitutions, deletions and
  insertions of predefined tags that we restored in the texts. 47.67\%
\end{compactdesc}
\noindent
\Tref{tbl:addfeats} reports the empirical improvement that each of
these brings independently when added to the main features
(\Sref{sec:mainfeats}).

>>>>

\begin{compactdesc}
\item[POS $n$-grams] Part-of-speech $n$-grams were used in various
  text-classification tasks.
\item[Prompt] Since the prompt contributes information on the domain,
  it is likely that some words (and, hence, character sequences) will
  occur more frequently with some prompts than with others. We
  therefore use the prompt ID in conjunction with other features.
\item[Document length] The number of tokens in the text is highly
  correlated with the author's level of fluency, which in turn is
  correlated with the author's L1.
\item[Pronouns] The use of pronoun varies greatly among different
  authors. We use the same list of~25 English pronouns that
  \citet{vered:noam:shuly} use for identifying translationese.
\item[Punctuation] Similarly, different languages use punctuation
  differently, and we expect this to taint the use of punctuation in
  non-native texts.
\item[Passives] English uses passive voice more frequently than other
  languages. Again, the use of passives in L2 can be correlated with
  the author's L1.
\item[Positional token frequency] The choice of the first and last few
  words in a sentence is highly constrained, and may be significantly
  influenced by the author's L1.
\item[Cohesive markers] These are 40 function words (and short
  phrases) that have a strong discourse function in texts (`however',
  `because', `in fact', etc.) Translators tend to spell out implicit
  utterances and render them explicitly in the target text
  \citep{Blum-Kulka:1986}. We use the list
  of~\citet{vered:noam:shuly}.
\item[Cohesive verbs] This is a list of manually compiled verbs that
  are used, like cohesive markers, to spell out implicit utterances
  (`indicate', `imply', `contain', etc.)
\item[Function words] Frequent tokens, which are mostly function
  words, have been used successfully for various text classification
  tasks. \citet{koppel-ordan:2011:ACL-HLT2011} define a list of 400
  such words, of which we only use~100 (using the entire list was not
  significantly different).
\item[Contextual function words] To further capitalize on the ability
  of function words to discriminate, we define pairs consisting of a
  function word from the list mentioned above, along with the POS tag
  of its adjacent word. This feature captures patterns such as verbs
  and the preposition or particle immediately to their right, or nouns
  and the determiner that precedes them. We also define 3-grams
  consisting of one or two function words and the POS tag of the third
  word in the 3-gram.
\item[Lemmas] The content of the text is not considered a good
  indication of the author's L1, but many text categorization tasks
  use lemmas (more precisely, the stems produced by the tagger) as
  features approximating the content.
\item[Misspelling features] Clearly, the spelling errors that learners
  make in English depend on the phonological properties of their
  L1. \sw{???}
\item[Restored tags] We focus on three important token classes defined
  above: punctuation marks, function words and cohesive verbs. We
  first remove words in these classes from the texts, and then recover
  the most likely hidden tokens \yt{To Shuly: I removed 'POS'. We recover words, not POS tags, I used the word 'tags' to distinguish between words to recover and all other words. Probably the word 'tag' is misleading, I changed it to 'token'} in a sequence of words, according to
  an $n$-gram language model trained on all essays in the training
  corpus corrected with a spell checker and containing both words and
  hidden tokens. This feature should capture specific words or
  punctuation marks that are consistently omitted (deletions), or
  misused (insertions, substitutions). To restore hidden tokens we use
  the \texttt{hidden-ngram} utility provided in SRILM
  \citep{stolcke02srilm}.
\item[Brown clusters] \sw{???}
\end{compactdesc}

@@

\begin{compactdesc}
\item[\feat{DocLen}] Document length in tokens. 11.81\%.
\item[\feat{Punct}] Counts of each punctuation mark. 27.41\%.
\item[\feat{Pron}] Counts of each pronoun. 22.81\%.
\item[\feat{Position}] Positional token frequency. We use the counts
  for the first two and last three words before the period in each
  sentence as features. 53.03\%.
\item[\feat{PsvRatio}] The proportion of passive verbs out of all
  verbs. 12.26\%.
\item[\feat{CxtFxn}] Contextual function words. Bi-grams yield
  62.79\%, tri-gram 62.32\%.
\item[\feat{Misspell}] Spelling correction edits. \sw{???}. 37.29\%.
\item[\feat{Restore}] Counts of substitutions, deletions and
  insertions of predefined tokens that we restored in the texts. 47.67\%
\end{compactdesc}
\noindent
\Tref{tbl:addfeats} reports the empirical improvement that each of
these brings independently when added to the main features
(\Sref{sec:mainfeats}).
